Simulation Deep Dive

### 2021-10-29 Simulation Deep Dive.Rmd
Added Rmd doc for simulation deep dive

source("OutlierCompNew.R")
library(ggplot2)
library(readr)
library(tibble)
library(dplyr)
library(tidyr)
library(janitor)
library(magrittr)
library(knitr)
library(Rtsne)
library(robustHD)
library(GGally)
library(stringr)
library(plotly)
library(R.utils)
library(vegan)
library(mnormt)

@@

# Multiple Groups

@@

@@

@@

# Larger

@@

@@

# Smaller

@@

# No Outliers

@@

mds1 <- readRDS("2021-10-19_simulationNone_mds_list.RDS")
tsne1 <- readRDS("2021-10-19_simulationNone_tsne_list.RDS")

@@

#t-SNE
ci1 <- sapply(df2list, spuriousInfluence)
cni1 <- 1-cni1

#MDS
ci2 <- sapply(df3list, spuriousInfluence)
cni2 <- 1 - cni2

@@

# One Group

>>>>

source("OutlierCompNew.R")
library(ggplot2)
library(readr)
library(tibble)
library(dplyr)
library(tidyr)
library(janitor)
library(magrittr)
library(knitr)
library(Rtsne)
library(robustHD)
library(GGally)
library(stringr)
library(plotly)
library(R.utils)
library(vegan)
library(mnormt)
library(MASS)

@@

# Multiple Groups - Uncorrelated

@@

The first section considers an influential point that bounces around within the variation of the three groups.  The means are different across the groups but there is no correlation between the 10 features simulated.

@@

#mean detection rates
Category <- c("Correctly Identified Influential", "Non-Influential")
TSNE <- c(mean(ci1), mean(cni1))
MDS <- c(mean(ci2), round(mean(cni2),3))
temp <- cbind(Category,TSNE, MDS)

kable(temp)

@@

# Larger - Uncorrelated

In this setting, we examine a case where the influential point is larger than the rest of the data. The data are still simulated in multiple groups.

@@

#mean detection rates
Category <- c("Correctly Identified Influential", "Non-Influential")
TSNE <- c(mean(ci1), round(mean(cni1),3))
MDS <- c(mean(ci2), round(mean(cni2),3))
temp <- cbind(Category,TSNE, MDS)

kable(temp)

@@

# Smaller - Uncorrelated

This setting should be quite similar to the results that we see in the larger influential point as the point is simply "flipped" to be several standard deviations smaller across the 10 features in the data.

@@

# No Outliers - Uncorrelated Data

@@

mds1 <- readRDS("2021-10-20_simulationNoInfluence_mds_list.RDS")
tsne1 <- readRDS("2021-10-20_simulationNoInfluence_tsne_list.RDS")

@@

#t-SNE
ci1 <- sapply(df2list, spuriousInfluence)
cni1 <- 1-ci1

#MDS
ci2 <- sapply(df3list, spuriousInfluence)
cni2 <- 1 - ci2

#mean detection rates
Category <- c("Correctly Identified Influential", "Non-Influential")
TSNE <- c(round(mean(ci1),3), round(mean(cni1),3))
MDS <- c(round(mean(ci2),3), round(mean(cni2),3))
temp <- cbind(Category,TSNE, MDS)

kable(temp)

@@

# Correlated Data

```{r}
n <- 10
  Sigma <- rWishart(1,n,diag(1,n)) %>% matrix(nrow = n, ncol = 10)
  diag(Sigma) <- 35

  g1 <- mvrnorm(n = 20, mu = rep(20, 10), Sigma)  %>%
    data.frame()
  g2 <- mvrnorm(n = 20, mu = rep(40, 10), Sigma) %>%
    data.frame()
  g3 <- mvrnorm(n = 20, mu = rep(60, 10), Sigma) %>%
    data.frame()

A heatmap of the variance-covariance matrix used to simulate the data is shown below. The correlations shift a little during the simulations because of the inverse-Wishart distribution used to generate the Sigma matrix at each round, but there are very few extreme correlations present - just some association between the features.

```{r}
image(Sigma, main = "Variance-Covariance Matrix of Features")

kable(Sigma)
```

**Results are pending** - simulation results are based on fewer runs.

```{r}

tsne1 <- readRDS("C:/Users/paulh/Documents/Doctoral Work/InfluenceInMaps/2021-10-24_simulationCorrelated_tsne_list2.RDS")
mds1 <- readRDS("C:/Users/paulh/Documents/Doctoral Work/InfluenceInMaps/2021-10-24_simulationCorrelated_mds_list2.RDS")

#mean detection rates
Category <- c("Correctly Identified Influential", "Non-Influential")
TSNE <- c(round(mean(ci1),3), round(mean(cni1),3))
MDS <- c(round(mean(ci2),3), round(mean(cni2),3))
temp <- cbind(Category,TSNE, MDS)

kable(temp)

# APPENDIX: ONE GROUP, THREE OUTLIERS
